---
title: "Final Report: Effects Of Kibble And Raw Meat Diets With Or Without Additives On Fecal Microbial Communities Of Healthy Adult Beagles"
author: "Emre Ovet"
date: "December 5, 2018"
output:
    github_document: default
bibliography: references.bib
csl: bioinformatics.csl
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Add about 2-3 pages here. Across the whole manuscript, you should cite at least 20 peer reviewed articles.

# Methods

## Study design

Add about half a page here. In this section instead of first person (I/we), use the authors of the paper you selected, since you'll just be describing what they did, based on the methods in their paper.

## Sample origin and sequencing

Add about half a page here. In this section instead of first person (I/we), use the authors of the paper you selected, since you'll just be describing what they did, based on the methods in their paper.

## Computational

These are the methods you used to do your bioinformatic analyses analyses. Should probably be between 0.5 and 1 pages. At a very minimum should include citations for DADA2 and phyloseq if you are doing an amplicon study, or other citations as appropriate.

# Results

## Subsections are ok in the results section too

```{r load-packages-and-data}
# load packages as needed
library("dplyr")
library("tidyr")
library("knitr")
library("ggplot2")
library("citr")
library("dada2")
library("seqinr")
library("mctoolsr")
library("phyloseq")

load("output/phyloseq_obj.Rdata")
load("output/melted_phyloseq.Rdata")
# load data produced from analysis scripts using
# something like load("output/processed_data.Rdata")
```



```{r}
melted_phyloseq %>%
  ggplot(aes(x = Phylum, y = Abundance, fill = food)) +
  geom_col(position = position_dodge()) +
  theme(axis.text = element_text(angle = 90, hjust = 1)) +
ggtitle("Abundance of Bacterial Phyla by Diet")
```

```{r}
melted_phyloseq %>%
  filter(food %in% c("chicken")) %>%
ggplot(aes(x = Phylum, y = Abundance, fill = additive)) +
  geom_col(position = position_dodge()) +
  theme(axis.text = element_text(angle = 90, hjust = 1)) +
ggtitle("Abundance of Bacterial Phyla in
       Chicken Diet With or Without Additives")
```

```{r}
melted_phyloseq %>%
  filter(food %in% c("beef")) %>%
ggplot(aes(x = Phylum, y = Abundance, fill = additive)) +
  geom_col(position = position_dodge()) +
  theme(axis.text = element_text(angle = 90, hjust = 1)) +
ggtitle("Abundance of Bacterial Phyla in Beef Diet With or Without Additives")
```

```{r}
melted_phyloseq %>%
  ggplot(aes(x = Family, y = Abundance, fill = food)) +
  geom_col(position = position_dodge()) +
  theme(axis.text = element_text(angle = 90, hjust = 1)) +
ggtitle("Abundance of Bacterial Family by Diet")
```

```{r}
melted_phyloseq %>%
  filter(food %in% c("chicken")) %>%
ggplot(aes(x = Family, y = Abundance, fill = additive)) +
  geom_col(position = position_dodge()) +
  theme(axis.text = element_text(angle = 90, hjust = 1)) +
ggtitle("Abundance of Bacterial Family in
       Chicken Diet With or Without Additives")
```

```{r}
melted_phyloseq %>%
  filter(food %in% c("beef")) %>%
ggplot(aes(x = Family, y = Abundance, fill = additive)) +
  geom_col(position = position_dodge()) +
  theme(axis.text = element_text(angle = 90, hjust = 1)) +
ggtitle("Abundance of Bacterial Family in Beef Diet With or Without Additives")
```

```{r}
melted_phyloseq %>%
  ggplot(aes(x = Genus, y = Abundance, fill = food)) +
  geom_col(position = position_dodge()) +
  theme(axis.text = element_text(angle = 90, hjust = 1)) +
ggtitle("Abundance of Bacterial Genus by Diet")
```

```{r}
melted_phyloseq %>%
  filter(food %in% c("chicken")) %>%
ggplot(aes(x = Genus, y = Abundance, fill = additive)) +
  geom_col(position = position_dodge()) +
  theme(axis.text = element_text(angle = 90, hjust = 1)) +
ggtitle("Abundance of Bacterial Genus in
       Chicken Diet With or Without Additives")
```

```{r}
melted_phyloseq %>%
  filter(food %in% c("beef")) %>%
ggplot(aes(x = Genus, y = Abundance, fill = additive)) +
  geom_col(position = position_dodge()) +
  theme(axis.text = element_text(angle = 90, hjust = 1)) +
ggtitle("Abundance of Bacterial Genus in Beef Diet With or Without Additives")
```


# Discussion

Add around 3-4 pages interpreting your results and considering future directions one might take in analyzing these data.

# Sources Cited
